Collocated Snapshot Backup with VM-Centric Deduplication in the Cloud

### 2013-09-25 snapshot_system/fast14_main.tex
revised
update
commented out authors

\documentclass[letterpaper,twocolumn,10pt]{article}
\usepackage{usenix}
\usepackage{mathptmx}
\usepackage[colorlinks,linkcolor=red,anchorcolor=blue,citecolor=green,urlcolor=black]{hyperref}
\usepackage{subfigure}
\usepackage{epsfig}
\usepackage{multirow}
\usepackage{array}
\usepackage{breqn}
\usepackage{pgfplots}
\usepackage{sansmath}
\pgfplotsset{compat=1.5}
\DeclareGraphicsExtensions{.pdf}

@@

\title{Collocated Deduplication with Fault Isolation for Virtual Machine Snapshot Backup [draft]}

\author{
  Wei Zhang$^{\star}$, Michael Agun$^\star$, Tao Yang$^\star$, and Hong Tang$^\dagger$ \\
  {\normalsize$^\star$  University of California at Santa Barbara}, {\normalsize$^\dagger$Alibaba Inc.} \\
  \{wei, tyang, dagun\}@cs.ucsb.edu, hongtang@alibaba-inc.com
}

>>>>

\documentclass[letterpaper,twocolumn,10pt]{article}
\usepackage{usenix}
\usepackage{mathptmx}
\usepackage[colorlinks,linkcolor=red,anchorcolor=blue,citecolor=green,urlcolor=black]{hyperref}
\usepackage{subfigure}
\usepackage{epsfig}
\usepackage{multirow}
\usepackage{array}
\usepackage{breqn}
\usepackage{pgfplots}
\usepackage{pgfplotstable}
\usepackage{sansmath}
\usepackage{booktabs}
\pgfplotsset{compat=1.5}
\DeclareGraphicsExtensions{.pdf}

@@

%\title{Collocated Deduplication with Fault Isolation for Virtual Machine Snapshot Backup [draft]}
\title{
Collocated Snapshot Backup with VM-Centric Deduplication in the Cloud}
%\author{
%  Wei Zhang$^{\star}$, Michael Agun$^\star$, Tao Yang$^\star$, and Hong Tang$^\dagger$ \\
%  {\normalsize$^\star$  University of California at Santa Barbara}, {\normalsize$^\dagger$Alibaba Inc.} \\
%  \{wei, tyang, dagun\}@cs.ucsb.edu, hongtang@alibaba-inc.com
%}
